\section{Overview}

This is the first lab of the semester. It is divided in three parts. In the first part, you will be measuring the values of the first two formants (F1 and F2) for English vowels. In the second part, you will be trying to find acoustic correlates of stop consonants in English. In the third and final part, you will be measuring acoustic information responsible for making the difference between voiced and unvoiced stop consonants like, for instance, between [b] and [p].

In order to perform these acoustic measurements, you'll be using \Praat{} on a set of files that are provided together with this document. \Praat{} is a free, cross--platform, open--source phonetic analysis package that can be downloaded from \href{http://www.praat.org}{http://www.praat.org}, and is straightforward to install. However, in case you have any difficulty installing \Praat{}, please do not hesitate to reach out to me.

\subsection{Deadlines and deliverables}

\paragraph{Part A:} Is due by \emph{Monday, February 19th, by midnight}, via the NYUClasses web interface. You should create a zip file containing your write up and the \filefmat{csv} file you created with your acoustic measurements.

\paragraph{Important:} There will \emph{no penalties} for handing in Part A of the lab after the deadline, as it was \emph{my fault} that you received this assignment late. Therefore, for this part of the lab, even if you hand it in late, you will have it back as soon as possible. However, please try to return the assignment by its due date, so you do not create a backlog of work for yourself, and it allows the class to follow a steady pace.

\paragraph{Parts B and C:} Are due by \emph{Monday, February 26th, by midnight}, via the NYUClasses web interface. You should create a zip file containing your write up and the spreadsheet file you created with your acoustic measurements.

